\tool: A Multi-Mode Attack Model of BadUSB

### 2021-01-21 WOOT/Files/experiment.tex
Power bank
Minor
Figures
[experiment] figure & case

@@

\subsubsection{Power bank sharing}

Power bank sharing provides users with short term rental of power banks. A provider deploys power bank stations in the city. Then, users can rent a power bank from any of the power bank station, charge their device on the trip, return the rented power bank to another station, and pay rent online.

@@

\begin{figure}[hbtp]
	\centering
	\includegraphics[width=.4 \linewidth]{./Figs/Brick_station.png}
	\includegraphics[width=.4 \linewidth]{./Figs/jiedian.jpg}
	\caption{Two power banks station products}
	\label{fig:PBS_products}
\end{figure}

@@

\subsubsection{QR code payment}

QR code payment is a payment method where payment is typically performed as the following steps:
\ding{182} The payer opens the payment application on his/her mobile device, and present his/her payment QR code to the payee. This QR code is encoded with a globally unique ID to identify the payer's account. 
\ding{183} The payee scan the payment QR code presented by the payer. By presenting this QR code, the payer authorizes proceeding with the payment.
\ding{184} An order generated by this scan is sent to the payment service provider. Then the payment service provider requests the payer to confirm the transaction.
\ding{185} After confirmation, the payment service provider proceed with this transaction and return the payment result to both the payee and the payer.

@@

It is worth noting that \tool exposed only a type-c cable (from USB Type-C hub),
and \tool will charge his or her device through this cable, which has no difference from ordinary power banks. Noticed the low users' vigilance and high similarity between \tool and normal power bank, the attacker can return his/her modified power bank (as \tool) to a power bank station, mixing \tool into the circulation of shared power banks. The next user unconsciously connect his/her device to \tool. 
He/She can find his/her devices being charged as normal.
Like many outdoor mobile phone usage scenarios, the victim may complete payment with showing payment code. In this process, the attacker can preemptively extract and use the victim's payment code to make another payment unknown to the victim, which threatens victim's property.

\subsection{User study}

In order to check what can be obtained by \tool, we conduct a user study in order to check the performance of \tool in Privacy extraction mode.

\subsubsection{Setup}

\subsubsection{Scenario}

We invited 6 volunteers to our lab room. Volunteers take turns to operate their phones for half an hour while \tool is connected. Before the study, we did not reveal the function of \tool and asked the volunteers to connect their phones to \tool as a normal power bank (ignoring its larger size). 
After the study, we told them our attack, checked recorded videos together, and confirmed the consent to study the information in recorded videos, Subject to efficiency reasons, we ask them to use phones like when they use the shared power bank outside.

@@

In terms of automatic analysis, OCR results of all frames are already stored in the database and can be used at hand. With these results, we can learn what issues the victim is browsing. Additionally, some keywords often appear with users' input data because they are often used as labels of input boxes, such as ``account'', ``username''. Such keywords are more likely to lead us to discover user-specific data. For example, in Figure~\ref{fig:ocr_keyword_example}, searching with ``account'' as the keyword, victim's accounts can be detected as shown in Fig. The frame number is the position of this frame in the recorded video, which indicates a target for manual analysis for further data extraction.

\begin{figure}[hbtp]
	\centering
	\includegraphics[width=\linewidth]{./Figs/ocr_keyword_example.png}
	\caption{Search ``account'' in all OCR results}
	\label{fig:ocr_keyword_example}
\end{figure}

@@

\begin{table*}[hbtp]
	\centering
	\begin{tabular}{|c|c|c|c|c|}
		\hline
		Application Column  & Application & Private information leaked                       \\
		\hline
		Finance App         & Alipay      & Alipay account, personal assets(blance)          \\
		\hline
		Social  Finance App & WeChat      & WeChat account, blance, chat history             \\
		\hline
		Social App          & QQ          & QQ account, interpersonal nexus, chat history    \\
		\hline
		Social App          & Twitter     & Twitter account, interpersonal nexus             \\
		\hline
		Social App          & Gmail       & Gmail account, mail records                      \\
		\hline
		Finance App         & ICBC        & ICBC account, password, personal assets(blance)  \\
		\hline
		Finance App         & Paypal      & Paypal account, blance, bank accounts            \\
		\hline
		Tool                & Chrome      & Sites visited                                    \\
		\hline
		Tool                & Health      & personal physical metrics      					 \\
		\hline
	\end{tabular}
	\linebreak
	\caption{Information extracted}
	\label{table:information_extracted}
\end{table*}

>>>>

\subsubsection{Background}

@@

\textbf{\textit{Power Bank Sharing}}. 
Power bank sharing provides users with short term rental of power banks. A provider deploys power bank stations in the city. Then, users can rent a power bank from any of the power bank station, charge their device on the trip, return the rented power bank to another station, and pay rent online.

@@

\begin{figure}[hbtp]
	\centering
	\includegraphics[width=.4 \linewidth]{./Figs/Brick_station.png}
	\includegraphics[width=.4 \linewidth]{./Figs/jiedian.jpg}
	\caption{Two power banks station products}\shuqing{Our attacking power banks.}
	\label{fig:PBS_products}
\end{figure}

@@

\textbf{\textit{QR Code Payment}}. 
QR code payment is a payment method where payment is typically performed as the following steps:
\ding{182} The payer opens the payment application on his/her mobile device, and present his/her payment QR code to the payee. This QR code is encoded with a globally unique ID to identify the payer's account. 
\ding{183} The payee scan the payment QR code presented by the payer. By presenting this QR code, the payer authorizes proceeding with the payment.
\ding{184} An order generated by this scan is sent to the payment service provider. Then the payment service provider requests the payer to confirm the transaction.
\ding{185} After confirmation, the payment service provider proceed with this transaction and return the payment result to both the payee and the payer.

@@

It is worth noting that \tool exposed only a type-c cable (from USB Type-C hub),
and \tool will charge his or her device through this cable, which has no difference from ordinary power banks. Noticed the low users' vigilance and high similarity between \tool and normal power bank, the attacker can return his/her modified power bank (as \tool) to a power bank station, mixing \tool into the circulation of shared power banks. The next user who unconsciously connect his/her device to \tool can find his/her devices being charged as normal.
Like many outdoor mobile phone usage scenarios, the victim may complete payment with showing payment code. In this process, the attacker can preemptively extract and use the victim's payment code to make another payment unknown to the victim, which threatens victim's property.

In order to check what can be obtained by \tool, we conduct a user study in order to check the performance of \tool in Privacy extraction mode. We invited 6 volunteers to our lab room. Volunteers take turns to operate their phones for half an hour while \tool is connected. Before the study, we did not reveal the function of \tool and asked the volunteers to connect their phones to \tool as a normal power bank (ignoring its larger size). 
After the study, we told them our attack, checked recorded videos together, and confirmed the consent to study the information in recorded videos, Subject to efficiency reasons, we ask them to use phones like when they use the shared power bank outside.

@@

In terms of automatic analysis, OCR results of all frames are already stored in the database and can be used at hand. With these results, we can learn what issues the victim is browsing. Additionally, some keywords often appear with users' input data because they are often used as labels of input boxes, such as ``account'', ``username''. Such keywords are more likely to lead us to discover user-specific data. For example, in Table~\ref{tab:ocr_keyword_example}, searching with ``account'' as the keyword, victim's accounts can be detected as shown in Fig. The frame number is the position of this frame in the recorded video, which indicates a target for manual analysis for further data extraction.

\begin{table*}[hbtp]
	\centering
	\begin{tabular}{|l|l|l|l|}
		\hline
		Keyword  & Text                                                                                                                          & Name                           & Frame Number \\ \hline
		username & X 8B cas.******.edu.cn Username: 117***18 Password:                                                                           & \textless{}user1\textgreater{} & 385          \\ \hline
		username & Login Weibo Login with SMS and verification code ...... +86 151****4587 Get verification code Login with username \& password & \textless{}user5\textgreater{} & 1947         \\ \hline
		username & QQ 14*****50| Login with phone number New user registration 2345678 9 0                                                       & \textless{}user3\textgreater{} & 4308         \\ \hline
		username & connect to *** username h*****l Save account information Open VPN.....                                                        & \textless{}user6\textgreater{} & 7925         \\ \hline
		+86      & Login with phone number ...... +86 186****2483 |                                                                              & \textless{}user1\textgreater{} & 313          \\ \hline
	\end{tabular}
	\caption{Example of searching OCR results with some keywords}
	\label{tab:ocr_keyword_example}
\end{table*}

@@

\begin{table*}[hbtp]
	\centering
	\begin{tabular}{|c|c|c|c|c|}
		\hline
		Application Column  & Application & Private information leaked                       \\
		\hline
		Finance App         & Alipay      & Alipay account, personal assets(blance)          \\
		\hline
		Social  Finance App & WeChat      & WeChat account, blance, chat history             \\
		\hline
		Social App          & QQ          & QQ account, interpersonal nexus, chat history    \\
		\hline
		Social App          & Twitter     & Twitter account, interpersonal nexus             \\
		\hline
		Social App          & Gmail       & Gmail account, mail records                      \\
		\hline
		Finance App         & ICBC        & ICBC account, password, personal assets(blance)  \\
		\hline
		Finance App         & Paypal      & Paypal account, blance, bank accounts            \\
		\hline
		Tool                & Chrome      & Sites visited                                    \\
		\hline
		Tool                & Health      & personal physical metrics      					 \\
		\hline
	\end{tabular}
	\linebreak
	\caption{Information extracted}\shuqing{Compress.}
	\label{table:information_extracted}
\end{table*}
